SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2019-01-13 frontrunning/Latex/sections/paper.tex
[frontrunning] add block stuffing attack ref
[frontrunning] batch auctions + authors + WIP watermark

We classify this in the unique category of a suppression attack in our taxonomy (see Section~\ref{sec:taxonomy}). At first glance, it seemed like an extreme version of an asymmetric/bulk displacement attack on any new ticket purchase transactions. However the key difference is that the front-runner does not care at all about the execution of her transactions---if miners mined empty blocks for three minutes, that would also be acceptable. Thus, bulk displacement is simply a means-to-an-end and not the actual end goal of the adversary.

@@

The final main category of mitigation is to assume front-running is unpreventable and to thus responsively redesign the functionality of the DApp to remove any benefit from it. For example, when designing a decentralized exchange, one can use a call market design instead of a time-sensitive order book~\cite{clark2014decentralizing} to side-step and disincentivize front-running. In a call market design, the arrival time of orders does not matter as they are executed in batches. The call market solution pivots profitable gains that front-running miners stand to gain into fees that they collect~\cite{clark2014decentralizing}, removing the financial incentive to front-run.

>>>>

We classify this in the unique category of a suppression attack in our taxonomy (see Section~\ref{sec:taxonomy}). At first glance, it seemed like an extreme version of an asymmetric/bulk displacement attack on any new ticket purchase transactions. However the key difference is that the front-runner does not care at all about the execution of her transactions---if miners mined empty blocks for three minutes, that would also be acceptable. Thus, bulk displacement\footnote{Also known as Block Stuffing Attack~\cite{blockstuffing18}} is simply a means-to-an-end and not the actual end goal of the adversary.

@@

The final main category of mitigation is to assume front-running is unpreventable and to thus responsively redesign the functionality of the DApp to remove any benefit from it. For example, when designing a decentralized exchange, one can use a call market design instead of a time-sensitive order book~\cite{clark2014decentralizing} to side-step and disincentivize front-running. In a call market design, the arrival time of orders does not matter as they are executed in batches\footnote{Also known as batch auctions~\cite{batchAuctions18}} . The call market solution pivots profitable gains that front-running miners stand to gain into fees that they collect~\cite{clark2014decentralizing}, removing the financial incentive to front-run.
